Model LF

### 2022-10-31 Final test.Rmd
Commit

```{r}
###Gengivelse af stød til model
max_dp_bs7b = Shock_bs7b$simulation$max_dp
wage_bs7b = Shock_bs7b$simulation$wage
komp_r_bs7b = Shock_bs7b$simulation$komp_r
part_bs7b = Shock_bs7b$simulation$part
yk_ds_bs7b = Shock_bs7b$simulation$yk_ds
pc_ds_bs7b = Shock_bs7b$simulation$pc_ds
wage_ds_t_bs7b = Shock_bs7b$simulation$wage_ds_t
ur_ds_bs7b = Shock_bs7b$simulation$ur_ds
emp_bs7b = Shock_bs7b$simulation$emp
yd_hk_ds_bs7b = Shock_bs7b$simulation$yd_hk_ds

tilpas_pr_bs7b = Shock_bs7b$simulation$tilpas_pr
u_ds_bs7b = Shock_bs7b$simulation$u_ds
part_bs7b = Shock_bs7b$simulation$part
nben_h_bs7b = Shock_bs7b$simulation$nben_h
wage_ds_bs7b = Shock_bs7b$simulation$wage_ds
dp_person_bs7b = Shock_bs7b$simulation$dp_person
kont_h_ratio_bs7b = Shock_bs7b$simulation$kont_h_ratio
lf_bs7b = Shock_bs7b$simulation$lf
nl_g_bs7b = Shock_bs7b$simulation$nl_g
unemp_bs7b = Shock_bs7b$simulation$unemp
yd_hk_ds_bs7b = Shock_bs7b$simulation$yd_hk_ds
wage_gap1_bs7b = Shock_bs7b$simulation$wage_gap1
wage_gap_bs7b = Shock_bs7b$simulation$wage_gap
prod_bs7b = Shock_bs7b$simulation$prod
ur_test_bs7b = Shock_bs7b$simulation$ur_test
ur_bs7b = Shock_bs7b$simulation$ur
```

@@

```{r}
plot(((emp_07 - emp_bs7)*1000), col= "blue", xlab= "Year", ylab= "Change in employment (people)", main= "Change in Employment", ylim= c(-5000, 300));
lines(((emp_04 - emp_bs4)*1000), col= "black");
lines(((emp_02 - emp_bs2)*1000), col= "red");
lines(((emp_01 - emp_00)*1000), col= "green");
legend("left", legend=c("All channels except productivity", "insurance rate channel", "wage channel", "demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```

@@

yk_ds_07b = Shock_7b$simulation$yk_ds
emp_07b = Shock_7b$simulation$emp
wage_ds_07b= Shock_7b$simulation$wage_ds
ur_ds_07b = Shock_7b$simulation$ur_ds
pc_ds_07b = Shock_7b$simulation$pc_ds
yd_hk_ds_07b = Shock_7b$simulation$yd_hk_ds
pconk_ds_07b = Shock_7b$simulation$pconk_ds
komp_r_07b = Shock_7b$simulation$komp_r
max_dp_07b = Shock_7b$simulation$max_dp
nben_h_07b = Shock_7b$simulation$nben_h
yd_hk_ds_07b = Shock_7b$simulation$yd_hk_ds
ik_07b = Shock_7b$simulation$ik
wage_ds_t_07b = Shock_7b$simulation$wage_ds_t
nben_h_un_07b = Shock_7b$simulation$nben_h_un
nl_g_07b = Shock_7b$simulation$nl_g
nsben_h_07b = Shock_7b$simulation$nsben_h
dp_person_07b = Shock_7b$simulation$dp_person
u_ds_07b = Shock_7b$simulation$u_ds
shock_kuld_07b = Shock_7b$simulation$shock_kuld
unemp_07b = Shock_7b$simulation$unemp
lf_07b = Shock_7b$simulation$lf
part_07b = Shock_7b$simulation$part
```

```{r}
plot(part_07b, col= "red"); lines(part_bs7b, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(ur_ds_07b, col= "red"); lines(ur_ds_bs7b, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

```{r}
plot(((emp_07b - emp_bs7b)*1000), col= "blue", xlab= "Year", ylab= "Change in employment (people)", main= "Change in Employment", ylim= c(-5000, 300));
lines(((emp_04 - emp_bs4)*1000), col= "black");
lines(((emp_02 - emp_bs2)*1000), col= "red");
lines(((emp_01 - emp_00)*1000), col= "green");
legend("left", legend=c("All channels except productivity", "insurance rate channel", "wage channel", "demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```

>>>>

```{r}
###Gengivelse af stød til model
max_dp_bs7b = Shock_bs7b$simulation$max_dp
wage_bs7b = Shock_bs7b$simulation$wage
komp_r_bs7b = Shock_bs7b$simulation$komp_r
part_bs7b = Shock_bs7b$simulation$part
yk_ds_bs7b = Shock_bs7b$simulation$yk_ds
pc_ds_bs7b = Shock_bs7b$simulation$pc_ds
wage_ds_t_bs7b = Shock_bs7b$simulation$wage_ds_t
ur_ds_bs7b = Shock_bs7b$simulation$ur_ds
emp_bs7b = Shock_bs7b$simulation$emp
yd_hk_ds_bs7b = Shock_bs7b$simulation$yd_hk_ds
prodk_bs7b = Shock_bs7b$simulation$prodk
tilpas_pr_bs7b = Shock_bs7b$simulation$tilpas_pr
u_ds_bs7b = Shock_bs7b$simulation$u_ds
part_bs7b = Shock_bs7b$simulation$part
nben_h_bs7b = Shock_bs7b$simulation$nben_h
wage_ds_bs7b = Shock_bs7b$simulation$wage_ds
dp_person_bs7b = Shock_bs7b$simulation$dp_person
kont_h_ratio_bs7b = Shock_bs7b$simulation$kont_h_ratio
lf_bs7b = Shock_bs7b$simulation$lf
nl_g_bs7b = Shock_bs7b$simulation$nl_g
unemp_bs7b = Shock_bs7b$simulation$unemp
yd_hk_ds_bs7b = Shock_bs7b$simulation$yd_hk_ds
wage_gap1_bs7b = Shock_bs7b$simulation$wage_gap1
wage_gap_bs7b = Shock_bs7b$simulation$wage_gap
prod_bs7b = Shock_bs7b$simulation$prod
ur_test_bs7b = Shock_bs7b$simulation$ur_test
ur_bs7b = Shock_bs7b$simulation$ur
```

@@

```{r}
plot(((unemp_07 - unemp_bs7)*1000), col= "blue", xlab= "Year", ylab= "Change in employment (people)", main= "Change in Employment", ylim= c(-300, 3000));
lines(((unemp_04 - unemp_bs4)*1000), col= "black");
lines(((unemp_02 - unemp_bs2)*1000), col= "red");
lines(((unemp_01 - unemp_00)*1000), col= "green");
legend("left", legend=c("All channels except productivity", "insurance rate channel", "wage channel", "demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```

@@

yk_ds_07b = Shock_7b$simulation$yk_ds
emp_07b = Shock_7b$simulation$emp
wage_ds_07b= Shock_7b$simulation$wage_ds
ur_ds_07b = Shock_7b$simulation$ur_ds
pc_ds_07b = Shock_7b$simulation$pc_ds
yd_hk_ds_07b = Shock_7b$simulation$yd_hk_ds
pconk_ds_07b = Shock_7b$simulation$pconk_ds
komp_r_07b = Shock_7b$simulation$komp_r
max_dp_07b = Shock_7b$simulation$max_dp
nben_h_07b = Shock_7b$simulation$nben_h
yd_hk_ds_07b = Shock_7b$simulation$yd_hk_ds
ik_07b = Shock_7b$simulation$ik
wage_ds_t_07b = Shock_7b$simulation$wage_ds_t
nben_h_un_07b = Shock_7b$simulation$nben_h_un
nl_g_07b = Shock_7b$simulation$nl_g
nsben_h_07b = Shock_7b$simulation$nsben_h
dp_person_07b = Shock_7b$simulation$dp_person
u_ds_07b = Shock_7b$simulation$u_ds
shock_kuld_07b = Shock_7b$simulation$shock_kuld
unemp_07b = Shock_7b$simulation$unemp
lf_07b = Shock_7b$simulation$lf
part_07b = Shock_7b$simulation$part

prodk_07b = Shock_7b$simulation$prodk
```

```{r}
plot(prodk_07b, col= "red"); lines(prodk_bs7b, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(ur_ds_07b, col= "red"); lines(ur_ds_bs7b, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(lf_07b, col= "red"); lines(lf_bs7b, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(yk_ds_07b, col= "red"); lines(yk_ds_07, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

```{r}
plot(((unemp_07b - unemp_bs7b)*1000), col= "blue", xlab= "Year", ylab= "Change in employment (people)", main= "Change in Employment", ylim= c(-300, 3000));
lines(((unemp_04 - unemp_bs4)*1000), col= "black");
lines(((unemp_02 - unemp_bs2)*1000), col= "red");
lines(((unemp_01 - unemp_00)*1000), col= "green");
legend("left", legend=c("All channels except productivity", "insurance rate channel", "wage channel", "demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```
